---
title: "Model exploration and interpretation (Assignment 9)"
output: html_document
---

For this assignment, I will be exploring and examining the *Grad School Admissions* data.

In order to accomplish the tasks for this assignment, the following packages were used:

```{r setup, include=FALSE}
library(tidyverse)
library(easystats)
library(ggplot2)
library(GGally)
library(modelr)
library(dplyr)
```

The first steps are to load the data and take a gander.

```{r import}
knitr::opts_chunk$set(echo = TRUE)
df=read.csv('Data/GradSchool_Admissions.csv')
str(df)
```

```{r view}
ggpairs(df)
```

##Models

Next, we make some models.

```{r models}
adm_mod=glm(data = df,formula=as.logical(admit)~gre,family = 'binomial')

adm_mod1=glm(data = df,formula=as.logical(admit)~gpa,family = 'binomial')

adm_mod2=glm(data=df,formula = as.logical(admit)~gre*gpa,family = 'binomial')

adm_mod3=glm(data=df,formula = as.logical(admit)~gre*gpa+rank,family = 'binomial')
```

We can then pull a report each of the models to see how they perform.

```{r report}
report(adm_mod)
report(adm_mod1)
report(adm_mod2)
report(adm_mod3)
```

##Model Comparison

Now that models have been made, we can compare their performance.

```{r performance}
compare_performance(adm_mod,adm_mod1,adm_mod2,adm_mod3, rank=TRUE)
```

As we can see from the Tjur's R2, none of the models are very good.

Then, we can graph them.

```{r performance plot}
plot(compare_performance(adm_mod,adm_mod1,adm_mod2,adm_mod3, rank=TRUE))
```

## Conclusion

Model 3 appears to be the best overall model for this data set; however, none of the models appear to predict admission with overwhelming success, indicating that there are other factors contributing to admission that are not included in the data set.